Indexes for measuring acute and chronic oak decline severity using phenotypic descriptors

### 2019-02-08 outline/outline.Rmd
added points to sections

---
title: "Indexes for measuring acute and chronic oak decline severity using phenotypic descriptors"
author: "Jasen Finch"
date: "07/02/2019"
output: pdf_document
---

@@

**Summary:** 
Two indexes, the phenotypic decline index (PDI) and the decline acuteness index (DAI), were developed to describe acute and chronic oak decline severity using a multitude of easily measureable phenotypic descriptors.
Measured phenotypic descriptors include aspects of tree shape and size, crown condition and the presence of biotic agents.
These were collected from 174 trees at 9 sites from across the south, east and west of England.
Between sites differences were identified as a results of aspects of tree size which were corrected for using a mean centering adjustment.
The decline indexes were then calculated using proximity values from an unsupervised random forest of the phenotypic descriptors, multidimensional scaling and min-max scaling.
These indexes are simple measures of tree decline severity allowing easy comparisons of oak trees both spatially and temporally providing a useful tool for forest monitoring and management.

@@

@@

###

@@

### Phenotypic descriptors

### Extended descriptors

@@

@@

### Comparison to assigned decline status labels

@@

>>>>

---
title: "Indexes for measuring acute and chronic oak decline severity using phenotypic descriptors"
output: pdf_document
---

@@

**Summary:** 
Two indexes, the Phenotypic Decline Index (PDI) and the Decline Acuteness Index (DAI), were developed to describe acute and chronic oak decline severity using a multitude of easily measureable phenotypic descriptors.
Measured phenotypic descriptors include aspects of tree shape and size, crown condition and the presence of biotic agents.
These were collected from 174 trees at 9 sites from across the south, east and west of England.
Between sites differences were identified as a results of aspects of tree size which were corrected for using a mean centering adjustment.
The decline indexes were then calculated using proximity values from an unsupervised random forest of the phenotypic descriptors, multidimensional scaling and min-max scaling.
These indexes are simple measures of tree decline severity allowing easy comparisons of oak trees both spatially and temporally providing a useful tool for forest monitoring and management.

@@

- Acute and chronic decline associated phenotypes

@@

### Data preparation and analysis

@@

### Phenotypic descriptors for oak decline

- Descriptions of collected phenotypic desciptors

- Definitions of additionally calculated features (crown condition, crown volume, bleed prevalence, *Agrillus* exit hole density)

@@

- Analysis of cross site differences
- Outline of cross site correction approach using mean centering adjustment

@@

- Association of phenotypic descriptors with manually assigned decline status
- Decline index calculation
- Comparison of indexes with manually assigned decline status labels

@@

- Disscusion of applications to forestry monitoring and management
